03-computation_issues

### 2019-02-25 journals/03-computation_issues/03-computation_issues.Rmd
started trying to use seriate to order the cases in the tile plots

>>>>

# Understanding `seriation`

The example below is from the paper "Getting Things in Order: An Introduction to the R Package seriation" by Hahsler, Hornik, and Buchta.

```{r}
library(seriation)

data("iris")
x <- as.matrix(iris[-5])
x <- x[sample(seq_len(nrow(x))), ]
d <- dist(x)
o <- seriate(d)
str(o)
class(0)
head(get_order(o), 15)
pimage(d, main = "Random")
pimage(d, o, main = "Reordered")
cbind(random = criterion(d), reordered = criterion(d, o))

pimage(x, main = "Random")
o_2mode <- c(o, ser_permutation(seq_len(ncol(x))))
pimage(x, o_2mode, main = "Reordered")
```

I wanted to learn how to use the order that is output from `seriate` to create my own plot using `ggplot`. I create a new dataframe below that includes the order and create two plots. Note that the "order" from `seriate`, which can be obtained using `get_order` is a vector with the case numbers ordered (not the order associated with a case).

```{r}
# Add a case variable (ordered by seriate order) and my own order variable to my dataframe
x2 <- data.frame(x) %>% 
  mutate(case = factor(1:n(), levels = get_order(o))) %>%
  arrange(case) %>%
  mutate(order = 1:n())

# Plot ordered using the case variable
x2 %>%
  gather(key = variable, value = value, 1:4) %>%
  ggplot(aes(x = variable, y = case, fill = value)) + 
  geom_tile()

# Plot ordered using the order variable
x2 %>%
  gather(key = variable, value = value, 1:4) %>%
  arrange(order) %>%
  ggplot(aes(x = variable, y = order, fill = value)) + 
  geom_tile()
```
